Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-09 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: reorganize subsub and subsection

@@

%%%%%%%%%%%%%%%%%
\subsection{Parameter Inference}

\subsubsection{Bayesian formalism}
If we assume that a GW signal observed in detector data $d$ is accurately
described by our waveform model \pSEOB{}, we can infer the parameters of the
model, $\bm{\lambda}$, given the hypothesis $\mathcal{H}$, using the Bayes
theorem,
%
\begin{equation}
P(\bm{\lambda} \vert d, \mathcal{H}) =
\frac{P(\bm{\lambda} \vert \mathcal{H}) \, P(d \vert \bm{\lambda},\mathcal{H})}{P(d \vert \mathcal{H})}\,,
\label{eq:bayes}
\end{equation}
%
where $P(\bm{\lambda} \vert d, \mathcal{H})$ is the posterior probability distribution,
$P(\bm{\lambda} \vert \mathcal{H})$ the prior,
$P(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
$P(d \vert \mathcal{H})$ the evidence.
%
The set of parameters, $\bm{\lambda}$ is the union between the GR waveform
model parameters~$\bm{\theta}$, detailed in Sec.~\ref{sec:review_pSEOB}, and
the non-GR parameter of $\ell$, i.e.,
%
\begin{equation}
\bm{\lambda} = \{\ell\} \cup \{\bm{\theta}\}.
\label{eq:def_params}
\end{equation}
%
which, we recall, set the characteristic lengthscale in which deviations from
GR become relevant in each of the theories described in
Sec.~\ref{sec:review_theories}.

@@

\subsubsection{Priors}

@@

\subsubsection{Event selection}

@@

\subsubsection{General remarks on the interpretation of our results}
\label{sec:remaks}

@@

\subsubsection{Stacking posteriors}
\label{sec:stack}

@@

\subsection{Results}

@@

\subsubsection{Einstein-dilaton-Gauss-Bonnet}
\label{sec:results_edgb}

@@

\subsubsection{Dynamical Chern-Simons}
\label{sec:results_dcs}

@@

\subsubsection{cubic effective-field-theory of general relativity}
\label{sec:results_ceft}

@@

\subsubsection{quartic effective-field-theory of general relativity}
\label{sec:results_qeft}

>>>>

%%%%%%%%%%%%%%%%%
\section{Parameter Inference}

@@

\subsection{Bayesian formalism}
If we assume that a GW signal observed in detector data $d$ is accurately
described by our waveform model \pSEOB{}, we can infer the parameters of the
model, $\bm{\lambda}$, given the hypothesis $\mathcal{H}$, using the Bayes
theorem,
%
\begin{equation}
P(\bm{\lambda} \vert d, \mathcal{H}) =
\frac{P(\bm{\lambda} \vert \mathcal{H}) \, P(d \vert \bm{\lambda},\mathcal{H})}{P(d \vert \mathcal{H})}\,,
\label{eq:bayes}
\end{equation}
%
where $P(\bm{\lambda} \vert d, \mathcal{H})$ is the posterior probability distribution,
$P(\bm{\lambda} \vert \mathcal{H})$ the prior,
$P(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
$P(d \vert \mathcal{H})$ the evidence.
%
The set of parameters, $\bm{\lambda}$ is the union between the GR waveform
model parameters~$\bm{\theta}$, detailed in Sec.~\ref{sec:review_pSEOB}, and
the non-GR parameter of $\ell$, i.e.,
%
\begin{equation}
\bm{\lambda} = \{\ell\} \cup \{\bm{\theta}\}.
\label{eq:def_params}
\end{equation}
%
which, we recall, set the characteristic lengthscale in which deviations from
GR become relevant in each of the theories described in
Sec.~\ref{sec:review_theories}.

@@

\subsection{Priors}

@@

\subsection{Event selection}

@@

\subsection{General remarks on the interpretation of our results}
\label{sec:remaks}

@@

\subsection{Stacking posteriors}
\label{sec:stack}

@@

@@

\subsection{Einstein-dilaton-Gauss-Bonnet}
\label{sec:results_edgb}

@@

\subsection{Dynamical Chern-Simons}
\label{sec:results_dcs}

@@

\subsection{cubic effective-field-theory of general relativity}
\label{sec:results_ceft}

@@

\subsection{quartic effective-field-theory of general relativity}
\label{sec:results_qeft}
